HMM Model development

### 2020-10-18 dev/hmm_model_devel.Rmd
One more level of optimization

```{r}
adapt_delta <- 0.9

data <- hmm_simulator(5, 10, 2, use_noisy_states = TRUE)

@@

model_single <- stan_model(model_code = single_code)

standata <- make_standata_hmm(data$observed)

>>>>

```{r}

adapt_delta <- 0.9

data <- hmm_simulator(N_series = 10, N_time = 12, N_mid_states = 4, use_noisy_states = FALSE)
standata <- make_standata_hmm(data$observed)

#Temporary hack
registerS3method("stan_log_lik", class = "rate_hmm", method = stan_log_lik.rate_hmm, envir = asNamespace("brms"))

@@

model_file <- here::here("local_temp_data", "devel_single_model.stan")
write_lines(single_code, path = model_file)
model_single <- cmdstanr::cmdstan_model(model_file)
